Impact of interaction network structure on community-level plant reproduction success

### 2019-03-19 paper_round2.Rmd
try to understand the code

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success. In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and [stability in the pollination service??]()

@@

At the community level, we followed the same logic as the one presented at the species level. Thus, we also calculated two network metrics providing complementary non-redundant information. In this case we focused on (i) nestedness and (ii) niche complementarity. Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003]. Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009]. However, many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance [@Song2017]. An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017]. We thus followed the advice provided by Song et al. (2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$. This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].

@@

d<-all_interactions
#head(d)
#I just realized here we are using all data available. 
#This is ok, but a few rare interactions are taken outside the transect (which can be removed?), and we are including focal 3' observations, which can be explained in methods.
#d <- subset(d, subset = Out != "out") #SHould we do that?
f<-fruitset
s<-seedset

@@

range01 <- function(x){(x-min(x))/(max(x)-min(x))}
f2_scaled_fruit <- f2 %>% group_by(Plant.sp) %>% mutate(tot.fruitset = range01(tot.fruitset))

#calculate average normalized fruitset values per site to have one unique value per site
f.ag.pr <- ddply(f2_scaled_fruit, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
              summarise, tot.visits    = sum(tot.visits),
              mean.fruitset = mean(tot.fruitset))

#select species with normalized values >0.5
f.ag_scaledb<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.50)

#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
f.ag_scaledb$no_rows<-rep(1, nrow(f.ag_scaledb))
f4c<- aggregate(no_rows ~ Site_ID, f.ag_scaledb, length)
head(f4c)

@@

f4e$species.pl<-out.site$species.pl[match(f4e$Site_ID, out.site$Site_id)]
#scale all variables

f4e$nodf.song.sc <- scale(f4e$nodf.song, center = T, scale = T)
f4e$functional.comp.poll.sc <- scale(f4e$functional.comp.poll, center = T, scale = T)
f4e$species.poll.sc <- scale(f4e$species.poll, center = T, scale = T)
f4e$tot.visits.sc <- scale(f4e$tot.visits, center = T, scale = T)
f4e$species.pl.sc <- scale(f4e$species.pl, center = T, scale = T)

@@

#I am removing them here.
f4 <- subset(f4, !Plant.sp %in% c("Astragalus lusitanicus", "Cistus albidus", "Anchusa azurea"))
#Alternative, we use raw values (not dividing by max.)

>>>>

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success. In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and [stability in the pollination service??]()

@@

At the community level, we followed the same logic as the one presented at the species level. Thus, we also calculated two network metrics providing complementary non-redundant information. In this case we focused on (i) nestedness and (ii) niche complementarity. Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003]. Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009]. However, many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance [@Song2017]. An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017]. We thus followed the advice provided by Song et al. (2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$. This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].[See new paper by Benno simons updating Song method :(]()

@@

d<-all_interactions
#head(d)
#I just realized here we are using all data available. 
#This is ok, but a few rare interactions are taken outside the transect (which can be removed?), and we are including focal 3' observations, which can be explained in methods.
#d <- subset(d, subset = Out != "out") #Should we do that?
f<-fruitset
s<-seedset

@@

range01 <- function(x){(x-min(x))/(max(x)-min(x))}
f2_scaled_fruit <- f2 %>% group_by(Plant.sp) %>% mutate(tot.fruitset = range01(tot.fruitset))
f2_scaled_fruit2 <- f2 %>% group_by(Plant.sp) %>% mutate(tot.fruitset = scale(tot.fruitset, center = TRUE, scale = TRUE))

#calculate average normalized fruitset values per site to have one unique value per site
f.ag.pr <- ddply(f2_scaled_fruit, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
              summarise, tot.visits    = sum(tot.visits),
              mean.fruitset = mean(tot.fruitset))
f.ag.pr2 <- ddply(f2_scaled_fruit2, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
              summarise, tot.visits    = sum(tot.visits),
              mean.fruitset = mean(tot.fruitset))
hist(f.ag.pr2$mean.fruitset)
#select species with normalized values >0.5
f.ag_scaledb<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.50)
f.ag_scaledb2<-subset(f.ag.pr2, f.ag.pr$mean.fruitset>0)

#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
f.ag_scaledb2$no_rows<-rep(1, nrow(f.ag_scaledb2))
f4c<- aggregate(no_rows ~ Site_ID, f.ag_scaledb2, length)
head(f4c)

@@

f4e$species.pl<-out.site$species.pl[match(f4e$Site_ID, out.site$Site_id)]
#scale all variables
f4e$nodf.song.sc <- scale(f4e$nodf.song, center = T, scale = T)
f4e$functional.comp.poll.sc <- scale(f4e$functional.comp.poll, center = T, scale = T)
f4e$species.poll.sc <- scale(f4e$species.poll, center = T, scale = T)
f4e$tot.visits.sc <- scale(f4e$tot.visits, center = T, scale = T)
f4e$species.pl.sc <- scale(f4e$species.pl, center = T, scale = T)

#Nacho depart##
#plot
plot(f4e$equity ~ f4e$functional.comp.poll.sc, las = 1)
#WARNING! Fails, because f4 (as calculated below) removes plants with n = 1 across trials). Hence 1.6 value...

m1 <- glm(equity ~  functional.comp.poll.sc , family="binomial", data=f4e)
m2 <- glm(cbind(no_rows, total.plant.numb) ~  functional.comp.poll.sc , family="binomial", data=f4e)
m3 <- glm(equity ~  functional.comp.poll.sc , weights = total.plant.numb, family="binomial", data=f4e)

summary(m1)
summary(m2)
summary(m3)
#bah...
####

@@

#I am removing them here.
f4 <- subset(f4, !Plant.sp %in% c("Astragalus lusitanicus", "Cistus albidus", "Anchusa azurea"))
#Alternative, we use raw values (not dividing by max. and scale. Thos will take value of 0, which is equally arbitrary...)
